What is happening on Twitter? Tweet analysis and undergraduate research projects

### 2020-05-26 Rmd/jse-special-issue-2020.Rmd
deleted backward design stuff

### Backward design

We sought to give our trainees opportunities to formulate and address a data science research question. We consulted the GAISE report for additional guidance. 
The GAISE report executive summary highlights six goals for statistics training:

1. Teach statistical thinking
1. Focus on conceptual understanding
1. Integrate real data with a context and purpose
1. Foster active learning
1. Use technology to explore concepts and analyze data
1. Use assessments to improve and evaluate student learning

### Learning outcomes

@@

### Parsing text of tweets

We used functions from the `rtweet` R package to parse tweet JSON into a data frame. 
We then divided tweet text into words with functions from the `tidytext` R package. We 
discarded commonly used "stop words" and emojis.

>>>>

@@

### Parsing tweet text

We used functions from the `rtweet` R package to parse tweet JSON into a data frame [@]. 
We then divided tweet text into words with functions from the `tidytext` R package. We 
discarded commonly used "stop words" and emojis.
